A pipeline to analyse time-course gene expression data

### 2019-10-29 scripts/manuscript.Rmd
Small fix on the manuscript

```{r visualize_scores, fig.height=6, fix.width=6}
# Get the best score for each gene
par(mfrow=c(4, 5))
scores = apply(scores_and_labels$scores, 1, min)
labels = apply(scores_and_labels$scores, 1, which.min)
for(cluster_id in 1:n_clusters){
    hist(scores[labels == cluster_id],
	 breaks=(1:50/50), xlim=c(0, 1),
	 col="black", main=paste("C", cluster_id, sep=""))
}

labels = unlist(labels[!is.na(labels)])

>>>>

```{r visualize_scores, fig.height=6, fix.width=6}
# Get the best score for each gene
par(mfrow=c(4, 5))
scores = apply(scores_and_labels$scores, 1, min)
labels = apply(scores_and_labels$scores, 1, which.min)
n_clusters = dim(kmeans_clusters$centroids)[1]
for(cluster_id in 1:n_clusters){
    hist(scores[labels == cluster_id],
	 breaks=(1:50/50), xlim=c(0, 1),
	 col="black", main=paste("C", cluster_id, sep=""))
}

labels = scores_and_labels$labels
labels = unlist(labels[!is.na(labels)])
